---
title: rCharts Dimple Integration
subtitle: Replicate Examples from dimplejs[http://dimplejs.org/examples_index.html]
author: Timely Portfolio
github: {user: timelyportfolio, repo: rCharts/dimple, branch: "gh-pages"}
framework: minimal
mode: selfcontained
ext_widgets: {rCharts: ["libraries/dimple"]}
hitheme: solarized_light
---

```{r echo = F, message = F, cache = F}
options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)
knitr::opts_chunk$set(
  comment = NA,
  results = 'asis',
  tidy = F,
  error = T,
  message = F,
  warning = F
)
```

```{r}
#require(devtools)
#install_github('rCharts', 'timelyportfolio', ref='test-dimple')
require(rCharts)

#get data used by dimple for all of its examples as a first test
data <- read.delim(
  "http://pmsi-alignalytics.github.io/dimple/data/example_data.tsv"
)

### eliminate . to avoid confusion in javascript
colnames(data) <- gsub("[.]","",colnames(data))
```

### example 1 vt bar
```{r}
d1 <- dPlot(
  x ="Month" ,
  y = "UnitSales",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(orderRule = "Date")
d1$publish()
```

### example 2 vt stacked bar
```{r}
d1 <- dPlot(
  x ="Month" ,
  y = "UnitSales",
  groups = "Channel",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(orderRule = "Date")
d1$set(
  legend = list(
    x = 60,
    y = 10,
    width = 700,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 3 vertical 100% bar
### use from above and just change y axis type
```{r}
d1$yAxis(type = "addPctAxis")
d1$publish()
```

### example 4 vertical grouped bar
```{r}
d1 <- dPlot(
  x = c("PriceTier","Channel"),
  y = "UnitSales",
  groups = "Channel",
  data = data,
  type = "dimple.plot.bar"
)
d1$set(
  legend = list(
    x = 60,
    y = 10,
    width = 700,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```

### example 5 vertical stack grouped bar
```{r}
d1 <- dPlot(
  x = c("PriceTier","Channel"),
  y = "UnitSales",
  groups = "Owner",
  data = data,
  type = "dimple.plot.bar"
)
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 6 vertical 100% Grouped Bar
### just change y Axis
```{r}
d1$yAxis(type = "addPctAxis")
d1$publish()
```

### example 7 horizontal bar
```{r}
d1 <- dPlot(
  Month ~ UnitSales,
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(type = "addMeasureAxis")
#good test of orderRule on y instead of x
d1$yAxis(type = "addCategoryAxis", orderRule = "Date")
d1$publish()
```


### example 8 horizontal stacked bar
```{r}
d1 <- dPlot(
  Month ~ UnitSales,
  groups = "Channel",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(type = "addMeasureAxis")
#good test of orderRule on y instead of x
d1$yAxis(type = "addCategoryAxis", orderRule = "Date")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```

### example 9 horizontal 100% bar
```{r}
d1$xAxis(type = "addPctAxis")
d1$publish()
```


### example 10 horizontal stacked bar
```{r}
d1 <- dPlot(
  x = "UnitSales", 
  y = c("PriceTier","Channel"),
  groups = "Channel",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(type = "addMeasureAxis")
#good test of orderRule on y instead of x
d1$yAxis(type = "addCategoryAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 11 horizontal stacked grouped bar
```{r}
d1 <- dPlot(
  x = "UnitSales", 
  y = c("PriceTier","Channel"),
  groups = "Owner",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(type = "addMeasureAxis")
#good test of orderRule on y instead of x
d1$yAxis(type = "addCategoryAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```

### example 12 horizontal 100% grouped bar
```{r}
d1$xAxis(type = "addPctAxis")
d1$publish()
```


### example 13 vertical marimekko
```{r}
d1 <- dPlot(
  UnitSales ~ Channel,
  groups = "Owner",
  data = data,
  type = "dimple.plot.bar"
)
d1$xAxis(type = "addAxis", measure = "UnitSales", showPercent = TRUE)
d1$yAxis(type = "addPctAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```

```{r}
### test with storyboard
d1$set(storyboard = "Date")
d1$publish()
```

### example 14 horizontal marimekko
```{r}
d1 <- dPlot(
  Channel ~ UnitSales,
  groups = "Owner",
  data = data,
  type = "dimple.plot.bar"
)
d1$yAxis(type = "addAxis", measure = "UnitSales", showPercent = TRUE)
d1$xAxis(type = "addPctAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 15 block matrix
```{r}
d1 <- dPlot(
  x = c("Channel","PriceTier"),
  y = "Owner",
  groups = "PriceTier",
  data = data,
  type = "dimple.plot.bar"
)
d1$yAxis(type = "addCategoryAxis")
d1$xAxis(type = "addCategoryAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 400,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 16 Scatter
```{r}
d1 <- dPlot(
  OperatingProfit~UnitSales,
  groups = c("SKU","Channel"),
  data = subset(data, Date == "01/12/2012"),
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addMeasureAxis" )
d1$yAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 17 Vertical Lollipop
```{r}
d1 <- dPlot(
  UnitSales ~ Month,
  groups = "Channel",
  data = data,
  type = "dimple.plot.bubble"
)
#defaults to yAxis (Measure) and xAxis (Category)
d1$xAxis( orderRule = "Date")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 18 Vertical Grouped Lollipop
```{r}
d1 <- dPlot(
  y = "UnitSales",
  x = c("PriceTier","Channel"),
  groups = "Channel",
  data = data,
  type = "dimple.plot.bubble"
)
#defaults to yAxis (Measure) and xAxis (Category)
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 19 Horizontal Lollipop
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = "Month",
  groups = "Channel",
  data = data,
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addMeasureAxis" )
d1$yAxis( type = "addCategoryAxis", orderRule = "Date")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 20 Horizontal Grouped Lollipop
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = c("PriceTier","Channel"),
  groups = "Channel",
  data = data,
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addMeasureAxis" )
d1$yAxis( type = "addCategoryAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 21 Dot Matrix
```{r}
d1 <- dPlot(
  y = "Owner",
  x = c("Channel","PriceTier"),
  groups = "PriceTier",
  data = data,
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addCategoryAxis" )
d1$yAxis( type = "addCategoryAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 22 Bubble
```{r}
d1 <- dPlot(
  x = "UnitSalesMonthlyChange",
  y = "PriceMonthlyChange",
  z = "OperatingProfit",
  groups = c("SKU","Channel"),
  data = subset(data, Date == "01/12/2012"),
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addMeasureAxis" )
d1$yAxis( type = "addMeasureAxis" )
d1$zAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 23 Vertical Bubble Lollipop
```{r}
d1 <- dPlot(
  x = "Month",
  y = "UnitSales",
  z = "OperatingProfit",
  groups = "Channel",
  data = subset(
    data,
    Date %in% c(
      "01/07/2012",
      "01/08/2012",
      "01/09/2012",
      "01/10/2012",
      "01/11/2012",
      "01/12/2012"
    )
  ),
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addCategoryAxis", orderRule = "Date" )
d1$yAxis( type = "addMeasureAxis" )
d1$zAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 24 Vertical Grouped Bubble Lollipop
```{r}
d1 <- dPlot(
  x = c("PriceTier","Channel"),
  y = "UnitSales",
  z = "OperatingProfit",
  groups = "Channel",
  data = subset(
    data,
    Date %in% c(
      "01/07/2012",
      "01/08/2012",
      "01/09/2012",
      "01/10/2012",
      "01/11/2012",
      "01/12/2012"
    )
  ),
  type = "dimple.plot.bubble"
)
d1$xAxis( type = "addCategoryAxis" )
d1$yAxis( type = "addMeasureAxis" )
d1$zAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 25 Horizontal Bubble Lollipop
```{r}
d1 <- dPlot(
  y = "Month",
  x = "UnitSales",
  z = "OperatingProfit",
  groups = "Channel",
  data = subset(
    data,
    Date %in% c(
      "01/07/2012",
      "01/08/2012",
      "01/09/2012",
      "01/10/2012",
      "01/11/2012",
      "01/12/2012"
    )
  ),
  type = "dimple.plot.bubble"
)
d1$yAxis( type = "addCategoryAxis", orderRule = "Date" )
d1$xAxis( type = "addMeasureAxis" )
d1$zAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


#### example 26 Horizontal Grouped Bubble Lollipop
```{r}
d1 <- dPlot(
  y = c("PriceTier","Channel"),
  x = "UnitSales",
  z = "OperatingProfit",
  groups = "Channel",
  data = subset(
    data,
    Date %in% c(
      "01/07/2012",
      "01/08/2012",
      "01/09/2012",
      "01/10/2012",
      "01/11/2012",
      "01/12/2012"
    )
  ),
  type = "dimple.plot.bubble"
)
d1$yAxis( type = "addCategoryAxis" )
d1$xAxis( type = "addMeasureAxis" )
d1$zAxis( type = "addMeasureAxis" )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 27 Bubble Matrix
```{r}
d1 <- dPlot(
  x = c( "Channel", "PriceTier"),
  y = "Owner",
  z = "Distribution",
  groups = "PriceTier",
  data = data,
  type = "dimple.plot.bubble",
  aggregate = "dimple.aggregateMethod.max"
)
d1$xAxis( type = "addCategoryAxis" )
d1$yAxis( type = "addCategoryAxis" )
d1$zAxis( type = "addMeasureAxis", overrideMax = 200 )
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 28 Area
```{r}
d1 <- dPlot(
  UnitSales ~ Month,
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area"
)
d1$xAxis(type = "addCategoryAxis", orderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$publish()
```


### example 29 Stacked Area
```{r}
d1 <- dPlot(
  UnitSales ~ Month,
  groups = "Channel",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area"
)
d1$xAxis(type = "addCategoryAxis", orderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 30 100% Stacked Area
### just change type for y axis
```{r}
d1$yAxis( type = "addPctAxis" )
d1$publish()
```



### example 31 Grouped Area
```{r}
d1 <- dPlot(
  y = "UnitSales",
  x = c("Owner","Month"),
  groups = "Owner",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area"
)
d1$xAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 32 Grouped Stacked Area
```{r}
d1 <- dPlot(
  y = "UnitSales",
  x = c("Owner","Month"),
  groups = "SKU",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area",
  bounds = list(x=70,y=30,height=340,width=330),
  barGap = 0.05,
  lineWeight = 1,
  height = 400,
  width = 590
)
d1$xAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$set(
  legend = list(
    x = 430,
    y = 20,
    width = 100,
    height = 300,
    horizontalAlign = "left"
  )
)
d1$publish()
```


### example 33 Grouped 100% Area
```{r}
d1$yAxis( type = "addPctAxis" )
d1$publish()
```


### example 34 Vertical Area
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = "Month",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area",
  bounds = list(x=80,y=30,height=480,width=330),
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", orderRule = "Date")
d1$publish()
```



### example 35 Vertical Stacked Area
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = "Month",
  groups = "Channel",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area",
  bounds = list(x=80,y=30,height=480,width=330),
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$set(
  legend = list(
    x = 60,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 36 Vertical 100% Stacked Area
```{r}
d1$xAxis(type = "addPctAxis")
d1$publish()
```


### example 37 Vertical Grouped Area
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = c("Owner","Month"),
  groups = "Owner",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area",
  bounds = list(x=90,y=30,height=470,width=330),
  lineWeight = 1,
  barGap = 0.05,
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$publish()
```

### example 38 Vertical Grouped Stacked Area
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = c("Owner","Month"),
  groups = "SKU",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.area",
  bounds = list(x=90,y=30,height=320,width=330),
  lineWeight = 1,
  barGap = 0.05,
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$set(
  legend = list(
    x = 430,
    y = 20,
    width = 100,
    height = 300,
    horizontalAlign = "left"
  )
)
d1$publish()
```


### example 39 Vertical Group 100% Area
```{r}
d1$xAxis( type = "addPctAxis" )
d1$publish()
```




### example 40 Line
```{r}
d1 <- dPlot(
  UnitSales ~ Month,
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line"
)
d1$xAxis(type = "addCategoryAxis", orderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$publish()
```

### example 41 Multiple Line
```{r}
d1 <- dPlot(
  UnitSales ~ Month,
  groups = "Channel",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line"
)
d1$xAxis(type = "addCategoryAxis", orderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$set(
  legend = list(
    x = 200,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```

### example 42 Grouped Single Line
```{r}
d1 <- dPlot(
  y = "UnitSales",
  x = c("Owner","Month"),
  groups = "Owner",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  barGap = 0.05
)
d1$xAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$publish()
```


### example 43 Grouped Multiple line
```{r}
d1 <- dPlot(
  y = "UnitSales",
  x = c("Owner","Month"),
  groups = "Brand",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  bounds = list(x=70,y=30,height=420,width=330),
  barGap = 0.05,
  height = 400,
  width = 590
)
d1$xAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$yAxis(type = "addMeasureAxis")
d1$set(
  legend = list(
    x = 510,
    y = 20,
    width = 100,
    height = 300,
    horizontalAlign = "left"
  )
)
d1$publish()
```


### example 44 Vertical Line
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = "Month",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  bounds = list(x=80,y=30,height=480,width=330),
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", orderRule = "Date")
d1$publish()
```



### example 45 Vertical Multiple Line
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = "Month",
  groups = "Channel",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  bounds = list(x=80,y=30,height=480,width=330),
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", orderRule = "Date")
d1$set(
  legend = list(
    x = 60,
    y = 10,
    width = 500,
    height = 20,
    horizontalAlign = "right"
  )
)
d1$publish()
```


### example 46 Vertical Grouped Line
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = c("Owner","Month"),
  groups = "Owner",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  bounds = list(x=90,y=30,height=470,width=330),
  barGap = 0.05,
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$publish()
```



### example 47 Vertical Grouped Multi Line
```{r}
d1 <- dPlot(
  x = "UnitSales",
  y = c("Owner","Month"),
  groups = "Brand",
  data = subset(data, Owner %in% c("Aperture","Black Mesa")),
  type = "dimple.plot.line",
  bounds = list(x=90,y=30,height=320,width=330),
  barGap = 0.05,
  height = 400,
  width = 590
)
d1$xAxis(type = "addMeasureAxis")
d1$yAxis(type = "addCategoryAxis", grouporderRule = "Date")
d1$set(
  legend = list(
    x = 430,
    y = 20,
    width = 100,
    height = 300,
    horizontalAlign = "left"
  )
)
d1$publish()
```

